*Supplement* Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary

### 2024-01-26 supplement.qmd
added ES edits

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "*Supplement* Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      institute: [TBEP]
      correspondence: false
  - Edward T Sherwood:
      email: esherwood@tbep.org
      institute: [TBEP]
      correspondence: false

institute:
  - TBEP: Tampa Bay Estuary Program, 263 13th Ave S., Suite 350, St. Petersburg, Florida 33701 USA

@@

![Example of mixed effects models for the estimated number of days per year that temperature (red) or salinity (blue) were above or below thresholds of 30 $^\circ$C or 25 psu, respectively, from 1988 to 2022. The bottom row (black) shows the number of days when both temperature was above and salinity was below the thresholds. The models included station as a random effect for each bay segment, with grey lines indicating individual station trends, grey points as actual number of days, and thicker lines indicating the overall model fit. Slopes for significant models are shown in the bottom right of each facet. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.](figs/suppmixeff.png){#fig-suppmixeff}

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "*Supplement* Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      institute: [TBEP]
      correspondence: false
  - Bradley T Furman:
      email: Bradley.Furman@myfwc.com
      institute: [FWRI]
      correspondence: false
  - David J Karlen: 
      email: karlen@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Chris Pratt: 
      email: prattc@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Edward T Sherwood:
      email: esherwood@tbep.org
      institute: [TBEP]
      correspondence: false

institute:
  - TBEP: Tampa Bay Estuary Program, 263 13th Ave S., Suite 350, St. Petersburg, Florida 33701 USA
  - FWRI: Florida Fish and Wildlife Conservation Commission, Florida Fish and Wildlife Research Institute, 100 8th Avenue SE, St. Petersburg, FL 33701, USA
  - EPCHC: Environmental Protection Commission of Hillsborough County, 3629 Queen Palm Drive, Tampa, FL 33619, USA

@@

![Example of mixed effects models for the estimated number of days per year that temperature (red) or salinity (blue) were above or below thresholds of 30 $^\circ$C or 25 psu, respectively, from 1988 to 2022. The bottom row (black) shows the number of days when both temperature was above and salinity was below the thresholds. The models included station as a random effect for each bay segment, with grey lines indicating individual station trends, grey points as actual number of days, and thicker lines indicating the overall model fit. Slopes for significant models are shown in the bottom left of each facet. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.](figs/suppmixeff.png){#fig-suppmixeff}
